Predicting Covid Data

### 2022-12-06 main.rmd
updates slides

Apply $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.

@@

* create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
- add more...

@@

"Each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations"

@@

## Applying the function to the whole cases dataset

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(cases_plot_Australia)
```

## Applying the function to the whole fatalities dataset

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(fatalities_plot_Australia)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(cases_plot_Australia + geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed"))
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(fatalities_plot_Australia + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed"))
```

>>>>

Apply an $nls$ function to determine the nonlinear (weighted) least-squares estimates of the four parameters $a,b,c,d$ of a Gauss error function model: $a+b*erf(c*x-d)$.

@@

* Create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* Each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j*
- Add more...

@@

- Each red dot corresponds to the day of occurrence of the flex obtained with each of the 150 Monte Carlo simulations

@@

@@

## Applying the function to the future cases dataset

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
cases_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
    scale_x_continuous(breaks = seq(0, 200, 10)) +
    xlim(0, 200) +
    labs(title = "Extrapolating Future Case Data with Gauss Error Function", x = "Days", y = "Total Cases")
fatalities_plot_Australia_future <- ggplot(australiaPre, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
    scale_x_continuous(breaks = seq(0, 200, 10)) +
    xlim(0, 200) +
    labs(title = "Extrapolating Future Fatality Data with Gauss Error Function", x = "Days", y = "Total Deaths")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(cases_plot_Australia_future)
```

## Applying the function to the future fatalities dataset

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(fatalities_plot_Australia_future)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(cases_plot_Australia_future + geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed") + labs(title="Day of flex indicator for cases (60 days after)"))
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(fatalities_plot_Australia_future + geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + labs(title="Day of flex indicator for fatalities (81 days after)"))
```

# Confirming Results with entire dataset

## Entire data (Cases)

```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
cases_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_cases)) + 
    geom_point() + 
    stat_function(fun=cases_function_australia, color="#d33636", size=1.5) +
    scale_x_continuous(breaks = seq(0, 200, 10)) +
    geom_vline(xintercept = mean(day_of_flex_ca), color="#d33636", size=1.5, linetype="dashed")
    labs(title = "Entire Cases in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Cases")
fatalities_plot_Australia_confirm <- ggplot(australia, aes(x = days, y = total_deaths)) +
    geom_point() + 
    stat_function(fun=fatalities_function_australia, color="#1b95ff", size=1.5) +
    scale_x_continuous(breaks = seq(0, 200, 10)) +
    geom_vline(xintercept = mean(day_of_flex_fa), color="#1b95ff", size=1.5, linetype="dashed") + 
    labs(title = "Entire Fatalities in Australia from 6/2/2020 to 12/18/2020 (200 days)", x = "Days", y = "Total Deaths")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(cases_plot_Australia_confirm)
```

## Entire data (Fatalities)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(fatalities_plot_Australia_confirm)
```

# Interesting Anomaly with United States Data

## All Data (Cases)

```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
# US data
us <- data %>% filter(location == "United States")
us <- subset(us, select = c(date, total_cases, total_deaths))
us <- us %>% mutate(days = 1:n())
us <- us %>% mutate(year = substr(date, 1, 4))
us_data_cases <- ggplot(data=us, aes(x=days, y=total_cases, color=year)) + 
  geom_point() + 
  labs(title="Total Cases in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Cases")
us_data_deaths <- ggplot(data=us, aes(x=days, y=total_deaths, color=year)) + 
  geom_point() + 
  labs(title="Total Deaths in the United States from 1/22/2020 to 11/14/2022 (1,028 days)", color="Year", x="Days", y="Total Deaths")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(us_data_cases)
```

## All Data (Fatalities)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
print(us_data_deaths)
```

## Conclusion
